resistanceModelNotesAndy

### 2015-04-16 resistanceModelNotesAndy.Rmd
progress notes

**15/4/15** wed 1.30-2.30 1hrs 3.45-

@@

1. see setInputSensiScenarios
1. start to write script to run sensitivity analysis, probably by creating a large input object rather than a large input.params.csv.

@@

1. ask Ian if he has the code for the Barbosa classification trees analysis.

1. from the first stage of the sensitivity analysis I'll want to output a dataframe with 1 row per replicate containing both the inputs and the outputs. Getting it to put the inputs into a dataframe like this would be a good start.

>>>>

**15/4/15** wed 1.30-2.30 1hrs 3.45-6.15 2.5 3.5hrs

setInputSensiScenarios
function to create sensitivity analysis scenarios, probably by creating a large input object.

**16/4/15** thurs 10-14 4hrs 2.30-5 2.5 6.5hrs

To get input params into 1 row per scenario I can transpose, but the result is a matrix and has no names.
But I need to find a way of getting column names set.

```{r}
input <- setInputSensiScenarios( nScenarios=3, P_1=c(0,0.5), P_2=c(0,0.5) )
tinput <- t(input)
str(tinput)
#num [1:3, 1:52] 100 100 100 100 100 100 1 1 1 0 ...
```

putting names into `setInputOneScenario()` fixed this.

Having a problem with sensiAnalysis1()
Error in eval(..1) : ..1 used in an incorrect context, no ... to look in

This may be because setInputSensiScenarios() expects a range for each argument, whereas setInputOneScenario expects a single value for the same named args. (but I don't really think it is this)

Also stackoverflow pointed that using c for a varname (and there is one in resistance) is dangerous because R can expect the function.

replaced c with recomb_rate for "Recombination Rate" to avoid R conflicts with c() 
previous ... error still remained

Aha! i think problem is that I specify defaults in setInputSensiScenarios when I don't need to (and that stops them making it into the ...)

cool yes, getting there.

@@

1. continue with getting classificatrion trees working in sensiAn1

1. update R, new lengths() function may be useful for me
but doesn't find latest version yet
library(installr)
updateR()

1. in susana's script the 'outcome' is 0/1 if used in our case that would seem to lose a lot of information about the outcomes ? Even timeToFifty would be better for us.

@@

1. from the first stage of the sensitivity analysis I'll want to output a dataframe with 1 row per replicate containing both the inputs and the outputs. Getting it to put the inputs into a dataframe like this would be a good start. I think this may just be a case of transposing the input object ?

1. try out classification trees code from Susana

1. maybe add option in setInputSensiScenarios to save input object as a csv or rda.
